Preregistered as Code: Gender differences in Machiavellianism

### 2021-08-08 README.Rmd
use cache when reproduce this manuscript
repro::automate()
change status to active

---
output: github_document
---

@@

# A Hitchhiker's Guide to Reproducible Research
<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

WIP

@@

>>>>

---
output: github_document
repro:
  images:
    - images/nutshell.svg
---

@@

# A Hitchhiker's Guide to Reproducible Research
<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

@@

## Abstract

```{r abstract, child = 'abstract.Rmd'}
```

```{r, echo=FALSE}
knitr::include_graphics("images/nutshell.svg")
```
